An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-14 paper.tex
Proofed marker section.

\subsection*{Markers}
%
We make use of the full body 47 marker set described in \cite{Bogert2013}
and presented in detail in Table \ref{tab:marker-labels}. As with all camera
based motion capture systems, the markers sometimes go missing in the
recording.

If the data was recorded in a D-Flow version less than 3.16.2rc4 [3], D-Flow
records the last non-missing value in all three axes until the marker is
visible again when a marker goes missing.

In D-Flow versions greater than or equal to 3.16.2rc4 the missing markers are
indicated in the TSV file as either 0.000000 or -0.000000, which is the same as
has been in the HBM columns in all versions of D-Flow. The D-Flow version must
be provided in the meta data yml file, otherwise it will assume D-Flow is at
the latest version.

@@

  \cprotect\caption{Descriptions of the 47 markers used in this study. The Set
    column indicates whether the marker exists in the lower and/or full body
    marker set.  The label column matches the column headers in the

>>>>

\subsection*{Markers}
%
We make use of the full body 47 marker set described in \cite{Bogert2013} and
presented in detail in Table \ref{tab:marker-labels}. As with all camera based
motion capture systems, the markers sometimes go missing in the recording. When
a marker goes missing, if the data was recorded in a D-Flow version less than
3.16.2rc4 [3], D-Flow continues to record the last non-missing value in all
three axes until the marker is visible again. In D-Flow versions greater than
or equal to 3.16.2rc4, the missing markers are indicated in the TSV file as
either \verb|0.000000| or \verb|-0.000000|, which is the same as has been in
the HBM columns in all versions of D-Flow. The D-Flow version must be provided
in the meta data yml file for each trial to be able to distinguish this detail.
%

@@

  \cprotect\caption{Descriptions of the 47 markers used in this study. The
    ``Set'' column indicates whether the marker exists in the lower and/or full
    body marker set. The label column matches the column headers in the
